\section{Drinfeld modular forms}


\subsection{Set the stage}

\begin{frame} \frametitle{The Drinfeld setting}
  We now move from the classical setting to that of function field arithmetic.
  % Most of the data are analogous with more familiar objects:

  \textbf{Function field object} \hfill \textbf{Classical analogue} \pause \\
  $F$, a fixed global function field \hfill $\QQ$, the rational numbers \pause \\
  $\abs{\cdot}$, a fixed absolute value on $F$ with associated place $\infty$ \hfill the usual absolute value $\abs{\cdot}$ on $\CC$ \pause \\
  $A$, the ring of elements of $F$ regular away from $\infty$ \hfill $\ZZ$, the integers \pause \\
  $\FF_\infty$, the completion of $F$ with respect to $\abs{\cdot}$ \hfill $\RR$, the real numbers \pause \\
  $\CC_\infty$, the completion of an algebraic closure of $\FF_\infty$ \hfill $\CC$, the complex numbers \pause

  Here, analogously with the classical setting, $A$ is a Dedekind ring.
  We also consider the positive integer $q$, which is the cardinality of the field of constants of $F$, with associated finite field $\FF_q$.
\end{frame}


\subsection{The only constant is change}

\begin{frame} \frametitle{Differences to the classical setting}
  In contrast with the classical setting, there are some key differences: \pause
  \begin{itemize}
    \item The main rings are of finite characteristic. \pause
    \item The absolute value $\abs{\cdot}$ is \emph{non-archimedean}; hence analytic issues such as convergence of series are in some ways easier, whereas defining an analytic function is more complex than in the classical case. \pause
    % \item As previously mentioned, lattices can have arbitrarily high integer rank. \pause
    \item In general, the elements of $A$ do not uniquely factorise into products of prime elements. However, since $A$ is a Dedekind ring we do have unique factorisation of \emph{ideals} into products of prime ideals. \pause So we henceforth let $N$ be an arbitrary proper ideal of $A$.
    \item Here $\CC_\infty$ has infinite dimension as a vector space over $\FF_\infty$, whereas $\CC$ has dimension $2$ as a vector space over $\RR$. \pause
    As a result, whereas lattices in the classical case can have rank at most $2$, here lattices can have arbitrarily high rank. This what makes the theory of `modular forms of higher rank' possible.
  \end{itemize}
\end{frame}


\subsection{What am I even doing?}

\begin{frame} \frametitle{My work -- higher rank}
  Whereas most of the theory of Drinfeld modular forms has focused on modular forms of rank $2$, due to the simplicity of dealing with a function of one variable, recent work by Gekeler (for $\FF_q(T)$) and Basson, Breuer, and Pink (for general $F$) have established theories of Drinfeld modular forms of higher rank. \pause
  
  Their approach has been viewing them as functions of $r-1$ variables, whereas my PhD thesis established a theory viewing them as functions on the space of lattices of higher rank. \pause
  My current work in this area is filling out the theory from this point of view.

  % Additionally, in the rank 2 case there is the question of generators for the (graded) algebra of modular forms for the principal congruence subgroup $\Gamma(N)$, where I have some partial computational results.
\end{frame}


\begin{frame} \frametitle{Lattices}
  \begin{definition}
    A lattice $\Lambda$ of rank $r$ is a projective $A$-submodule of $\CC_\infty$ of rank $r$ \pause (\ie a subset of $\CC_\infty$ of the form $I_1\psi_1 +\dotsb +I_r\psi_r$ for ideals $I_i \subseteq A$ and $\psi_i \in \CC_\infty$ which are $\FF_\infty$-linearly independent). \pause

    A level $N$ structure for a lattice $\Lambda$ of rank $r$ is an $A$-module bijection $\parens{N^{-1}/A}^r \ionto N^{-1}\Lambda/\Lambda$.
  \end{definition} \pause

  Every lattice has $\size{\GL[r]{A/N}}$ different level $N$ structures, since $A$ is a Dedekind ring.

  We denote the space of lattices $\Lambda$ of rank $r$ with level $N$ structure $\alpha$ by $\LL_N^r$, and the space of lattices $\Lambda$ of rank $r$ without level structure by $\LL^r$. \pause
  % The left action of $\gamma \in \GL[2]{A/N}$ on $\LL_N^r$ is given by
  % \[ \gamma(\Lambda,\alpha) \defeq (\Lambda, \alpha \circ \gamma^{-1}). \]

  We prove that these spaces are rigid analytic spaces by identifying them with a double quotient:
  \[ \LL_N^r \simeq \left. \GL[r]{F} \middle\backslash \parens{\Psi^r \times \GL[r]{\AA_F^{fin}}/K(N)} \right. \]
  and so we can speak of holomorphic functions on these spaces.
\end{frame}


\begin{frame} \frametitle{Higher rank modular forms} \pause
  We define metrics $\dd_\LL$ and $\dd_{\LL_N^r}$ on the rigid analytic spaces $\LL^r$ and $\LL_N^r$, leading to their completions $\LL^{\leq r}$ and $\LLNRi$, where the boundaries consist of spaces of lattices of lower rank. \pause
  \begin{definition} \label{def:strongMForm}
    A \emph{modular form} of \emph{weight} $k$ and \emph{rank} $r$ for $K(N)$ is a function $f : \LLNRi \to \CCi$ which is: \pause
    \begin{itemize}
      \item holomorphic on the interior $\LL_N^r$ of $\LLNRi$\pause,
      \item homogeneous of degree $-k$\pause, and
      \item continuous on $\LLNRi$. \pause
    \end{itemize}
  \end{definition}

  % The left action of $\gamma \in \GL[2]{A/N}$ on $\LLNRi$ translates to a right action on the space of modular forms, by $f|_\gamma(\Lambda,\alpha) = f(\Lambda, \alpha \circ \gamma^{-1})$.

  My PhD thesis was on the general theory of modular forms of higher rank as functions of lattices, and I am currently extending this theory in the following areas: \pause
  \begin{itemize}
    \item Proving that modular forms have Fourier-type series expansions at cusps \pause
    \item Defining Hecke operators and proving their recursive properties
  \end{itemize}
\end{frame}


\begin{frame} \frametitle{My work -- Eisenstein series in rank $2$} \pause
  Typical examples of modular forms of rank $2$ for $\Gamma(N)$ are the (partial) Eisenstein series:
  \[ E_{r_1,r_2}(z) = \sum_{m,n \in A} \frac{1}{(m+r_1)z+n+r_2} \lsptext{for} r_1,r_2 \in N^{-1}A/A; \]
  here we are considering the case of $A = \FF_q[T]$. \pause

  Cornelissen proved that the graded algebra of Drinfeld modular forms of rank $2$ for $\Gamma(N)$ are generated by these Eisenstein series and possibly some cusp forms of weight $2$, but it is not known whether or not these cusp forms are necessary. \pause
  
  I have some partial computational results in this direction: for specific $N$ we can reduce it to linear algebra using the series expansions of these Eisenstein series at the cusps and the known dimension of the space of weight $2$ modular forms, but I hope to finish it off analytically.
\end{frame}